---
title: "M06 Reflection: Revealjs and Advanced Data Wrangling"
author: "Frank Renn"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-link: true
    code-fold: show
    code-tools: true
    code-overflow: wrap
    embed-resources: true
editor: visual
execute:
  echo: true
  freeze: auto
---

# In **Step 1**, you learned how to design stunning presentation slides with Quarto. What's your impression of the Revealjs presentation? Describe its capabilities as you learned from the presentations. What are its strengths and weaknesses compared with PPT?

Revealjs combines slides, code, tables, charts, speaker notes, citations, transitions, fragments, and a table of contents in one Quarto file. It is especially useful for analytical work because the results can be regenerated from code.

Its main strengths over PPT are reproducibility, web-based publishing, and integration with R and Markdown. Its weaknesses are the steeper learning curve, dependence on YAML and code, and less flexible object-level design. PPT is easier for free-form visual editing and familiar to most users, while Revealjs is better for transparent, data-driven presentations.

# In **Step 2**, you were asked to create a Revealjs presentation. **Provide a link to the presentation you published on the web**.

> **Presentation link:** [Open the local presentation file](Avenue_Shabu_CEP_Revealjs_Presentation.html). Replace this local link with the published Quarto Pub or GitHub Pages URL before submission.

## Add at least one reproducible chart or table in the presentation.

The presentation includes a reproducible customer-summary table created from a small R tibble. The table demonstrates how customer identifiers, visits, spending, and segments can be organized before CRM analysis.

## Briefly describe what the presentation is about.

The presentation introduces the Avenue Shabu CEP project. It focuses on using Toast customer and transaction data to understand repeat visits and support targeted email/SMS marketing. The proposed workflow includes customer identification, RFM-style measures, segmentation, campaign recommendations, and measurement of repeat visits and revenue.

## What did you learn from the experience of the Revealjs presentation?

I learned that presentation design should begin with the business problem and analytics objective. Revealjs also showed me how code can make tables and results reproducible. I learned that fragments and speaker notes improve delivery, while YAML settings and browser-based formatting require more technical attention than PPT.

# My advanced wrangling lecture in **Step 3** introduced new concepts, including how to join relational databases. Pick three different functions, each from a different category. Describe when to use them and give one coding example along with an output for each function. To clarify, you are expected to do literate programming to weave your narratives with the code.

## `left_join()` — mutating relational join

Use `left_join()` to add columns from a related table while preserving every row in the main table. This is useful when visit records need customer segments or profile information.

```{r}
library(dplyr)
library(knitr)

visits <- tibble(
  customer_id = c("A01", "A02", "A04"),
  visits = c(5, 2, 1)
)

segments <- tibble(
  customer_id = c("A01", "A02", "A03"),
  segment = c("high-value", "active", "at-risk")
)

left_join(visits, segments, by = "customer_id") |>
  kable()
```

Output:

| customer_id | visits | segment    |
|:------------|-------:|:-----------|
| A01         |      5 | high-value |
| A02         |      2 | active     |
| A04         |      1 | NA         |

`A04` remains in the result because it exists in the left table, but its unmatched segment becomes `NA`.

## `across()` — column-wise operation

Use `across()` when the same transformation should be applied to several columns. It reduces repeated code and is useful for preparing multiple RFM measures.

```{r}
rfm <- tibble(
  customer_id = c("A01", "A02", "A03"),
  recency = c(12, 45, 8),
  frequency = c(5, 2, 9),
  monetary = c(210, 85, 320)
)

rfm |>
  mutate(
    across(
      c(recency, frequency, monetary),
      ~ round(.x / max(.x) * 100, 1),
      .names = "{.col}_index"
    )
  ) |>
  kable()
```

Output:

| customer_id | recency | frequency | monetary | recency_index | frequency_index | monetary_index |
|:----------|----------:|----------:|----------:|----------:|----------:|----------:|
| A01 | 12 | 5 | 210 | 26.7 | 55.6 | 65.6 |
| A02 | 45 | 2 | 85 | 100.0 | 22.2 | 26.6 |
| A03 | 8 | 9 | 320 | 17.8 | 100.0 | 100.0 |

The example demonstrates the mechanics of `across()`. A production RFM score would normally reverse the recency direction because fewer days since the last visit is better.

## `row_number()` — ranking function

Use `row_number()` to assign a sequential position after sorting observations. It can identify the top customers or the first records within a grouped analysis.

```{r}
customer_visits <- tibble(
  customer_id = c("A01", "A02", "A03", "A04"),
  visits = c(5, 2, 7, 2)
)

customer_visits |>
  arrange(desc(visits), customer_id) |>
  mutate(rank = row_number()) |>
  kable()
```

Output:

| customer_id | visits | rank |
|:------------|-------:|-----:|
| A03         |      7 |    1 |
| A01         |      5 |    2 |
| A02         |      2 |    3 |
| A04         |      2 |    4 |

The secondary sort by `customer_id` makes tied visit counts deterministic. If tied customers should receive the same rank, `min_rank()` or `dense_rank()` would be more appropriate.